Comparison of Dimensionality Reduction Schemes for Parallel Global Optimization Algorithms

### 2018-09-23 2018/RSD/MultiEvolvents/slides/slides.tex
RSD: update slides

@@

\begin{frame}
  \frametitle{Choice of evolvent for the parallel algorithm}
  \begin{table}
  \begin{center}
  \caption{Averaged number of computations of \(g_0\) and of \(\varphi\) when solving the
  problems from GKLS 3d Simple class using the shifted evolvent}
    \begin{tabular}{|l|{c}|{c}|{c}|}
      \hline
    $L$ & $calc(g_0)$ & $calc(\varphi)$ & $\frac{calc(g_0)}{calc(\varphi)}$ ratio \\
    \hline
    2 & 96247.9  & 6840.14 & 14.07\\
    \hline
    3 & 153131.0 & 7702.82 & 19.88\\
    \hline
    \end{tabular}
    \label{tab:shifted_g0}
  \end{center}
  \end{table}
\end{frame}

@@

\begin{frame}
  \frametitle{Conclusions}
    %Already done:
    \begin{itemize}
      \item the smooth evolvent and the non-univalent one demonstrate the best result in the problems of small dimensionality and can be applied successfully in solving the problems with the computational costly objective functions.
      \item the shifted evolvents introduce large overhead costs on the execution of the method due to the requirement to adding an auxiliary constraint. About 95\% of iterations are overhead to fight the auxiliary constraint.
      \item rotated evolvents perform almost the same as the shifted ones but without overhead.
      \item parallel optimization method shows up to 33x speedup on hard \(5d\) problems when using a set of rotated evolvents.
    \end{itemize}
    %Future work:
    %\begin{itemize}
    %  \item
    %\end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Parallel optimization method with multiple evolvents}
  \begin{figure}[ht]
    \includegraphics[width=0.95\textwidth]{evolvents_parallel.pdf}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Choice of evolvent for the parallel algorithm}
  \begin{itemize}
    \item Smooth evolvent is too computational heavy.
    \item Non-univalent evolvent generates large and unpredictable amount of preimages.
    \item Shifted evolvent generates huge amount of auxiliary points to handle additional constraint.
  \end{itemize}
  \begin{table}
  \begin{center}
  \caption{Averaged number of computations of \(g_0\) and of \(\varphi\) when solving the
  problems from GKLS 3d Simple class using the shifted evolvent}
    \begin{tabular}{|l|{c}|{c}|{c}|}
      \hline
    $L$ & $calc(g_0)$ & $calc(\varphi)$ & $\frac{calc(g_0)}{calc(\varphi)}$ ratio \\
    \hline
    2 & 96247.9  & 6840.14 & 14.07\\
    \hline
    3 & 153131.0 & 7702.82 & 19.88\\
    \hline
    \end{tabular}
    \label{tab:shifted_g0}
  \end{center}
  \end{table}
\end{frame}

@@

\begin{frame}
  \frametitle{Conclusions}
    %Already done:
    \begin{itemize}
      \item The smooth evolvent and the non-univalent one demonstrate the best result in the problems of small dimensionality and can be applied successfully in solving the problems with the computational costly objective functions.
      \item The shifted evolvents introduce large overhead costs on the execution of the method due to the requirement to adding an auxiliary constraint. About 95\% of iterations are overhead to fight the auxiliary constraint.
      \item Rotated evolvents perform almost the same as the shifted ones but without overhead.
      \item Parallel optimization method shows up to 43x speedup on hard \(5d\) problems when using a set of rotated evolvents.
    \end{itemize}
    %Future work:
    %\begin{itemize}
    %  \item
    %\end{itemize}
\end{frame}
